% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Ongoing}  {Project Engineer and Data scientist}{Medellin}{Logistica y ATP}
    {April 2019} {
                      \begin{itemize}
                        \item Developing model algorithms for logistics application.                      
                        \item Estimating the duration and costs of projects.                  
                        \item Analyzing customer data to propose efficient solutions that improve processes along the supply chain.               
                        \item Developing and maintaining Warehouse design                                                                
                      \end{itemize}
                    }
                    {Python, Pyspark, E-Commerce, SQL}
  \emptySeparator
  \experience
    {March 2019} {Coordinator of Application Engineering}{Medellin}{Colplast S.A.S.}
    {March 2018}    {
                      \begin{itemize}
                        \item Formulated, designed and controlled the projects of the sub-management for the development, implementation, testing, and production concerning plastics transformation.                           
                        \item Determined the scope of the project together with technicians and engineers, to establish the activities and resources required for its successful completion.                        
                      \end{itemize}
                    }
                    {Python, Project}
  \emptySeparator
  \experience
    {March 2018}     {Mechanical Maintenance and Project Engineer}{Medellin}{Plastiquimia S.A.S}
    {August 2017}    
                    {
                      \begin{itemize}
                        \item I created an Excel and Python program capable for anticipating the company energy cost per machine.
                        \item I created several applications that help with the maintenance and management in Excel.               
                        \item Developed detailed 3D modeling using Solidworks, Auto Rhinoceros.                  
                                                 
                      \end{itemize}
                    }
                    {Python, Oracle DB, SQL, Excel}
  \emptySeparator
  \experience
  {September 2012}       {Mould and die design apprentice}{Medellin}{TECNOMEC S.A.S}
  {January 2014}
                    {
                      \begin{itemize}
                        \item 3D modeling and detailed engineering in CAD programs (Solidworks and Auto Rhinoceros).                              
                        \item Programming macros and applications in Excel.           
                     
                      \end{itemize}
                    }
                    {Python, Excel,SQL,Solidworks}
  
  \emptySeparator            

\end{experiences}
